TGI-spinal-power

### 2022-05-09 analysis/tgispine_lme_power.Rmd
zero inflated beta regression models for cold and warm

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)

@@

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)
```

@@

# Summarise data per rating, per participant
sum_burn <- aggregate(burn~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
sum_warm <- aggregate(warm~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
sum_cold <- aggregate(cold~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
# then compile all data again
sum_burn$VAS = 'burn'
names(sum_burn)[6] <- 'rating'
sum_warm$VAS = 'warm'
names(sum_warm)[6] <- 'rating'
sum_cold$VAS = 'cold'
names(sum_cold)[6] <- 'rating'
df_sum <- rbind(sum_cold, sum_warm)
df_sum <- rbind(df_sum, sum_burn)

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
# first the simplest model
model.cold <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID), 
                   data = df_sum[df_sum$VAS == 'cold' ,])
# then adding procedure as a fiexed effect
model.cold2 <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID) + (1|procedure), 
                   data = df_sum[df_sum$VAS == 'cold' ,])
# then modelling slope of the subjects
model.cold3 <- lmer(rating ~ manipulation + condition + cold_location +
                     (1+manipulation|ID) + (1|procedure), 
                   data = df_sum[df_sum$VAS == 'cold' ,])

# summarise all 3 models
modelsummary(list(model.cold, model.cold2, model.cold3),
             gof_map = gof_stuff)
```
# View the coefficients for each person (should vary, due to random slope model)

@@

Now let's do the same for warm!
# Warm model
```{r}
model.warm <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID),
                   data = df_sum[df_sum$VAS == 'warm' ,])
summary(model.warm)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)

@@

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)
```
Need to change this and create two cold models - one with zero inflated and one without
Also need to check Bayesian
- Check out Jesper's code

@@

# Summarise data per rating, per participant
sum_burn <- aggregate(burn~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
sum_warm <- aggregate(warm~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
sum_cold <- aggregate(cold~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
# then compile all data again
sum_burn$VAS = 'burn'
names(sum_burn)[6] <- 'rating'
sum_warm$VAS = 'warm'
names(sum_warm)[6] <- 'rating'
sum_cold$VAS = 'cold'
names(sum_cold)[6] <- 'rating'
df_sum <- rbind(sum_cold, sum_warm)
df_sum <- rbind(df_sum, sum_burn)
```

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(rating ~ manipulation + condition + cold_location + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_phs$warm)
# then model warm VAS
```
# Look at model assumptions
```{r}
model.cold.assmup <- simulateResiduals(model.cold)
plot(model.cold.assmup)
```

# View the coefficients for each person (should vary, due to random slope model)

@@

Now let's do the same for warm!
# Warm model
```{r}
model.warm <- lmerTest::lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID),
                   data = df_sum[df_sum$VAS == 'warm' ,])
summary(model.warm)
```
